---
title: "Flavors"
author: "Aashna Patel"
format: html
execute: 
  echo: false
  message: false
  warning: false
---

```{r}
library(tidyverse)
library(gganimate)
cheeses <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2024/2024-06-04/cheeses.csv')
```
This pie chart shows the distribution of flavors across France, Germany, and Italy combined. 

```{r}
cheese_counts <- cheeses %>%
  filter(flavor %in% c("creamy", "nutty", "mild", "tangy", "sweet", "sharp", "earthy", "buttery", "salty", "fruity")) %>%
  count(flavor) %>%
  arrange(desc(flavor))

cheese_counts <- cheese_counts %>%
  mutate(percent = n / sum(n) * 100)

# Plotting pie chart
ggplot(cheese_counts, aes(x = "", y = n, fill = flavor)) +
  geom_bar(stat = "identity", width = 1, color = "white") +
  geom_text(aes(label = paste0(round(percent), "%")), position = position_stack(vjust = 0.5))+  # Create pie chart using bar plot
  coord_polar("y", start = 0) +  # Convert bar plot to polar coordinates for pie chart
  labs(
    title = "Distribution of Flavors in Common Cheese Types",
    fill = "Flavor",
    caption = "Source: TidyTuesday - Cheeses Dataset"
  ) +
  theme_void() +  # Remove axis and grid lines
  scale_fill_viridis_d(option = "C", begin = 0.2, end = 0.8)  # Use viridis color palette
```


The pie chart displays the distribution of flavors like creamy, nutty, tangy, sweet, and others in common cheese types. It emphasizes creamy and nutty flavors as prevalent, guiding producers in meeting consumer preferences and diversifying product offerings effectively. 
Among teh flavors, creamy and nutty are the most popular. This helps cheese makers know what consumers prefer and make cheeses that people will want to buy.